Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-03-17 paper/results.tex
Update graphics.
Add ROC curve and update conclusion.
Minor fixes

%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
Please note that additional plots are available as supplemental material due to reasons of space.

@@

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{gfx/precisionrecall.pdf}
\caption{Precision-recall curves comparing focused proofreading (FP) and our guided proofreading (GP) classifiers. We evaluate on unbalanced tests sets of the AC4 subvolume (darker colors) and the L. Cylinder volume (lighter colors). GP performs better.}
\label{fig:pr}
\end{figure}

@@

\begin{table}[h]
\caption{Average proofreading speed for novice users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP). Our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP, while being slightly slower per correction.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
\makecell{Approach\\(Novice)} & \makecell{Time Per\\Correction (s)} & \makecell{VI Reduction\\Per Minute} & \makecell{Improvement} \\
\midrule
\emph{Dojo} & 30.5 & -0.00200 & $-8.7\times$ \\
%\emph{Dojo Expert?} & xxx & xxx \\
\emph{FP} & 4.9 & 0.00023 & $1.0\times$\\
\emph{GP} & 6.2 & 0.00173 & $7.5\times$\\
\bottomrule
\end{tabular} 
}
\label{tab:correctiontimes}
\end{table}

>>>>

%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.
Additional plots are available as supplemental material due to limited space.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{gfx/roc.pdf}
\caption{Receiver Operating Characteristic curves comparing focused proofreading and guided proofreading automatic correction. We evaluate on unbalanced tests sets of the AC4 subvolume (darker colors) and the L. Cylinder volume (lighter colors). Guided proofreading performs better.}
\label{fig:pr}
\end{figure}

@@

\begin{table}[t]
\caption{Average proofreading speed for novice users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP). Our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP, while being slightly slower per correction.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
\makecell{Approach\\(Novice)} & \makecell{Time Per\\Correction (s)} & \makecell{VI Reduction\\Per Minute} & \makecell{Improvement} \\
\midrule
\emph{Dojo} & 30.5 & -0.00200 & $-8.7\times$ \\
%\emph{Dojo Expert?} & xxx & xxx \\
\emph{FP} & 4.9 & 0.00023 & $1.0\times$\\
\emph{GP} & 6.2 & 0.00173 & $7.5\times$\\
\bottomrule
\end{tabular} 
}
\label{tab:correctiontimes}
\end{table}
